Reflections from reproductions

### 2025-01-07 pages/reflections.qmd
docs(reflections): add version link to summary chart, and add counts of applicable criteria to wheel figures

It **excludes** the "Other section". It also excludes a few criteria which weren't felt particularly relevant/suitable to mark as met or not. These were "link publication to a specific version of the code", "optimise model run time" and "avoid large file sizes".

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
    'Share code with an open licence': [4, 0, 4, 0],
    'List required packages and versions': [0, 6, 2, 0],
    'Provide code for all scenarios<br>and sensitivity analyses': [1, 1, 5, 1],
    'Ensure model parameters are correct': [4, 2, 2, 0],
    'Control randomness': [5, 0, 3, 0],
    'Include code to calculate all<br>required model outputs': [3, 0, 5, 0],
    'Include code to generate the tables,<br>figures and other reported results': [1, 3, 4, 0],
    'Separate model code from applications': [1, 0, 1, 6],
    'Avoid hard-coded parameters': [3, 2, 2, 1],
    'Minimise code duplication': [5, 0, 3, 0],
    'Comment sufficiently': [1, 3, 4, 0],
    'Ensure clarity and consistency<br>in the model results tables': [5, 0, 3, 0],
    'Include run instructions': [2, 1, 5, 0],
    'State run times and<br>machine specifications': [0, 5, 3, 0],
    'Save output to a file': [4, 0, 4, 0],
    'Avoid excessive output files': [7, 0, 1, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T

>>>>

It **excludes** the "Other section". It also excludes a few criteria which weren't felt particularly relevant/suitable to mark as met or not. These were "optimise model run time" and "avoid large file sizes".

@@

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
criteria_dict = {
    'Share code with an open licence': [4, 0, 4, 0],
    'Link publication to a specific<br>version of the code': [0, 0, 2, 6],
    'List required packages and versions': [0, 6, 2, 0],
    'Provide code for all scenarios<br>and sensitivity analyses': [1, 1, 5, 1],
    'Ensure model parameters are correct': [4, 2, 2, 0],
    'Control randomness': [5, 0, 3, 0],
    'Include code to calculate all<br>required model outputs': [3, 0, 5, 0],
    'Include code to generate the tables,<br>figures and other reported results': [1, 3, 4, 0],
    'Separate model code from applications': [1, 0, 1, 6],
    'Avoid hard-coded parameters': [3, 2, 2, 1],
    'Minimise code duplication': [5, 0, 3, 0],
    'Comment sufficiently': [1, 3, 4, 0],
    'Ensure clarity and consistency<br>in the model results tables': [5, 0, 3, 0],
    'Include run instructions': [2, 1, 5, 0],
    'State run times and<br>machine specifications': [0, 5, 3, 0],
    'Save output to a file': [4, 0, 4, 0],
    'Avoid excessive output files': [7, 0, 1, 0]
}
criteria_wide = pd.DataFrame(criteria_dict, index=col).T
